---
title: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(htmltools)
library(datamaps)
library(dplyr)

cn <- unique(countrycode::countrycode_data$iso3c)
cn <- cn[!is.na(cn)]

data <- data.frame(name = cn, color = ceiling(runif(length(cn), 1, 50)))
```

<main>
<div class = "container">

```{r}
h1(
  "datamaps"
)
```


```{r}
data %>%
  datamaps(width = "100%") %>%
  add_choropleth(name, color, colors = c("#2196f3", "#bbdefb"))
```

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/datamaps.svg?branch=master)](https://travis-ci.org/JohnCoene/datamaps)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/JohnCoene/datamaps?branch=master&svg=true)](https://ci.appveyor.com/project/JohnCoene/datamaps)

```{r, echo = FALSE}
div(
  class = "row",
  div(
    class = "col m6",
    "R htmlwidget for ",
    a(
      "datamaps",
      href = "http://datamaps.github.io/",
      target = "_blank"
    )
  ),
  div(
    class = "col m3",
    a(
      class = "btn blue waves-effect",
      href="https://github.com/JohnCoene/datamaps", 
      target = "_blank",
      tags$i(
        class = "material-icons left",
        "code"
      ),
      "Repository"
    )
  ),
  div(
    class = "col m3",
    a(
      href = "http://shiny.john-coene.com/datamaps/",
      tagret = "_blank",
      class = "btn blue",
      tags$i(
        class = "material-icons left",
        "dashboard"
      ),
      "Proxy demo"
    )
  )
)
```

> Customizable SVG map visualizations for the web in a single Javascript file using D3.js

### Install 

```{r, echo = TRUE, eval = FALSE}
# install.packages("devtools")
devtools::install_github("JohnCoene/datamaps")
```

### How it works

Initiate your map with `datamaps`, pipe (`%>%`) your data to add data (`add_data`) or layers.

```{r}
tags$ul(
  class = "collection with-header",
  tags$li(
    class = "collection-header",
    tags$h5(
      "Layers"
    )
  ),
  tags$li(
    class = "collection-item",
    code("add_choropleth")
  ),
  tags$li(
    class = "collection-item",
    code("add_arcs"),
    " and ",
    code("add_arcs_name")
  ),
  tags$li(
    class = "collection-item",
    code("add_bubbles")
  ),
  tags$li(
    class = "collection-header",
    tags$h5(
      "Options"
    )
  ),
  tags$li(
    class = "collection-item",
    code("add_labels")
  ),
  tags$li(
    class = "collection-item",
    code("add_legend")
  ),
  tags$li(
    class = "collection-item",
    code("add_graticule")
  ),
  tags$li(
    class = "collection-item",
    code("config_geo")
  ),
  tags$li(
    class = "collection-item",
    code("config_bubbles")
  ),
  tags$li(
    class = "collection-item",
    code("config_arcs")
  )
)
```

### First map

```{r, echo = TRUE}
# Fake data
st <- c("AR", "NY", "CA", "IL", "CO", "MT", "TX", "OK", "AL", "NM", "NV", "NC", "OH", "PA")
states <- data.frame(from = st, to = sample(st, 14))

states %>%
    datamaps(scope = "usa", width = "100%") %>% # intiate map
    add_arcs_name(from, to) %>% # add arcs layers 
    add_labels() # add state labels
```

### Advanced examples

Below is the code used to generate the map in the header of this very page.

```{r, echo = TRUE, eval = FALSE}
cn <- unique(countrycode::countrycode_data$iso3c)
cn <- cn[!is.na(cn)]

data <- data.frame(name = cn, color = ceiling(runif(length(cn), 1, 50)))

data %>%
  datamaps() %>%
  add_choropleth(name, color)
```

Combine types.

```{r}
library(datamaps)
library(dplyr)

sesh <- read.csv("https://raw.githubusercontent.com/JohnCoene/projects/gh-pages/htmlwidgets/echarts/data/sessions.csv")

# datamaps uses iso3c format
sesh$iso3c <- countrycode::countrycode(sesh$Country, "country.name", "iso3c")
sesh <- sesh[!is.na(sesh$iso3c),] # remove NA
sesh$continent <- countrycode::countrycode(sesh$iso3c, "iso3c", "continent") # find continents

# sum Sessions by continent
continents <- sesh %>% 
  group_by(continent) %>% 
  summarise(Sessions = sum(Sessions)) %>% 
  mutate(long = c(3.917313, -99.133209, 106.660172, 16.363449),
         lat = c(7.401962, 19.432608, 10.762622, 48.210033))

sesh %>% 
  datamaps(default = "lightgray", width = "100%") %>% # initiate map
  add_choropleth(iso3c, Sessions, colors = RColorBrewer::brewer.pal(5, "YlOrRd")) %>% # add chorpleth layer
  add_data(continents) %>% # add continent dataset
  add_bubbles(long, lat, log(Sessions) * 5, continent, continent, colors = RColorBrewer::brewer.pal(4, "Set1")) # add continent bubbles
```

Set different projections and add graticule.

```{r}
data <- data.frame(name = c("USA", "CAN", "BRA", "ARG", "MEX", "CUB", "BOL"),
                   color = round(runif(7, 1, 10)))

data %>%
    datamaps(projection = "orthographic", width = "100%") %>%
    add_choropleth(name, color, colors = c("skyblue", "yellow", "orangered")) %>% 
  add_graticule() 
```

### Proxies

Shiny proxies to update the map without redrawing.

* `update_choropleth`
* `update_arcs`
* `update_arcs_name`
* `update_bubbles`

```{r, echo = FALSE}
a(
  href = "http://shiny.john-coene.com/datamaps/",
  tagret = "_blank",
  class = "btn blue pulse",
  "Proxy demo"
)
```

Proxy example

```{r, eval=FALSE, echo=TRUE}
library(shiny)

ui <- fluidPage(
  selectInput(
    "countrySelect",
    "Select Country",
    choices = c("USA", "FRA", "CHN", "RUS", "COG", "DZA", "BRA", "IND")
  ),
  sliderInput(
    "value",
    "Value",
    min = 1,
    max = 10,
    value = 5
  ),
  actionButton("update", "Update"),
  datamapsOutput("map")
)

server <- function(input, output){

  data <- data.frame(name = c("USA", "FRA", "CHN", "RUS", "COG", "DZA", "BRA", "IND", "ALG", "AFG"),
                     color = 1:10)

 updated_data <- reactive({
   data.frame(name = input$countrySelect, value = input$value)
 })

  output$map <- renderDatamaps({
    data %>%
      datamaps() %>%
      add_choropleth(name, color)
  })

  observeEvent(input$update, {
    datamapsProxy("map") %>%
      add_data(updated_data()) %>% # pass updated data
      update_choropleth(name, value, TRUE) # update
  })
}

shinyApp(ui, server)
```

</div>
</main>
