---
title: "fullpage"
author: "John Coene"
date: "June 12, 2017"
output: 
  reporter::fullpage_document:
    highlight: zenburn
    toc: true
    navigation: false
    background: 
      - '#3f51b5'
      - '#4db6ac'
      - '#9575cd'
      - '#7986cb'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmltools)
```


# Sections

## This is a section

This is a section.

Sections are marked by `h1` tags or `# Some Section` in `Rmarkdown`.

```{r, eval=FALSE}
# Sections

## This is a section

Sections are marked by `h1` tags or `# Some Section` in `Rmarkdown`.
```

# Slides

##### Slide 1

## This is Slide 1

You can also include slides.

Slides are `h5` or `##### Some Slide` in `Rmarkdown`.

```{r, eval=FALSE}
# Slides

##### Slide 1

## This is Slide 1

You can also include slides.

Slides are `h5` or `##### Some Slide` in `Rmarkdown`.
```

##### Slide 2

## This is Slide 2

Second slide content.

```{r, eval=FALSE}
##### Slide 2

## This is Slide 2

Second slide content.
```

# Colors

## Colors

You can set background colors with `background` in your `yaml`.
Below are the colors used for this document:

```{r, eval=FALSE}
background: 
  - '#3f51b5'
  - '#4db6ac'
  - '#9575cd'
  - '#7986cb'
```

# Options

## Options

There are many other options you can set up see the `r tags$a("documentation", href="http://john-coene.com/reporter", target = "_blank", style = "color: white;")` for the full list.