---
title: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmltools)
library(funplot)
library(dplyr)
```

<main>
<div class = "container">

```{r, echo=FALSE}
h1(
  "funplot",
  a(
    class = "github-button",
    href = "https://github.com/JohnCoene/funplot",
    `data-icon` = "octicon-star",
    `aria-label`= "Star JohnCoene/funplot on GitHub",
    `data-show-count` = TRUE,
    "Star"
  )
)
```

```{r, echo = FALSE}
funplot() %>%
  fun_add("x * x") %>%
  fun_deriv("2 * x", mouse = TRUE) %>%
  fun_add("x * x * x") %>%
  fun_secants(x0 = 5, mouse = TRUE)
```

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/funplot.svg?branch=master)](https://travis-ci.org/JohnCoene/funplot)

Function Plot is a plotting library built on top of D3.js used to render functions with little configuration (think of it as a clone of Google's plotting utility: y=x2)

The library currently supports interactive line charts and scatterplots, whenever the graph scale is modified the function is evaluated again with the new bounds, result: infinite graphs!

```{r, echo=FALSE}
p(
  a(
    class = "btn blue waves-effect",
    href="https://github.com/JohnCoene/funplot", 
    target = "_blank",
    tags$i(
      class = "material-icons left",
      "code"
    ),
    "Repository"
  )
)
```

### Install 

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("JohnCoene/funplot")
```

### Your first plot

Pass basic functions.

```{r}
funplot() %>%
  fun_add(fun = "sin(x)") 
```

### Parametric equations

Use parametric equations.

```{r}
funplot() %>%
  fun_add_param(
    x = "sin(t) * (exp(cos(t)) - 2 cos(4t) - sin(t/12)^5)",
    y = "cos(t) * (exp(cos(t)) - 2 cos(4t) - sin(t/12)^5)"
  )
```

### Polar equations

Use polar equations.

```{r}
funplot() %>%
  fun_add_polar(r = "2 * sin(4 theta)")
```

### Implicit functions

Use polar functions (see `fun_scope`).

```{r}
funplot() %>%
  fun_add_imp("x ^ 2 + y ^ 2 - 1")
```

### Multiple functions

Plot multiple equations.

```{r}
funplot() %>%
  fun_add("sqrt(1 - x * x)") %>%
  fun_add("-sqrt(1 - x * x)")
```

### Secants and derivatives

Chart in header of this page.

```{r}
funplot() %>%
  fun_add("x * x") %>%
  fun_deriv("2 * x", mouse = TRUE) %>%
  fun_add("x * x * x") %>%
  fun_secants(x0 = 5, mouse = TRUE)
```

### Math.js

function-plot uses interval-arithmetic math by default, unfortunately some functions are not implemented yet because of the underlying complexity, for this reason you can always evaluate a function with [math.js](http://mathjs.org/).

```{r}
funplot() %>%
  fun_math("tan(x)", samples = 4000) %>% 
  fun_x("log")
```

### Options

This is only some of the options.

```{r}
funplot() %>%
  fun_add("x^2", color = "orange") %>%
  fun_annot(x = 1, text = "x = 1") %>%
  fun_annot(y = 2, text = "y = 2") %>% 
  fun_y(label = "Y axis", domain = c(-1, 7)) %>% 
  fun_title("funplot options")
```


<script async defer src="https://buttons.github.io/buttons.js"></script>
</div>
</main>
