---
title: "mjml"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmltools)
library(mjml)
```

<main>
<div class = "container">

```{r, echo=FALSE}
h1(
  "mjml",
  a(
    class = "github-button",
    href = "https://github.com/JohnCoene/mjml",
    `data-icon` = "octicon-star",
    `aria-label`= "Star JohnCoene/mjml on GitHub",
    `data-show-count` = TRUE,
    "Star"
  )
)
```

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/mjml.svg?branch=master)](https://travis-ci.org/JohnCoene/mjml)

Easily create responsive emails from R with [mjml](https://mjml.io/).

### Setup

Install the package.

```{r, echo = TRUE, eval = FALSE}
devtools::install_github("JohnCoene/mjml") # dev version
```

Install [mjml](https://mjml.io/).

```{bash, eval = FALSE}
# Install with npm in a folder where you will use MJML
$> npm install mjml

# In the folder where you installed MJML you can now run:
$> ./node_modules/.bin/mjml -V
```

Point to mjml from R.

```{r}
mj_set("./node_modules/.bin/mjml")
```

You're set!

### Basics

```{r, eval = FALSE}
# create an email
mj_ml(
  mj_body(
    mj_container(
      mj_section(
        mj_column(
          mj_text("Some text"),
          mj_image(src = "https://media.vanityfair.com/photos/54cbf3da998d4de83ba3602a/master/w_960,c_limit/image.jpg")
        )
      )
    )
  )
) -> mjml

# save as mjml
mjml %>% 
  mj_save_mjml("email.mjml")

# save as mjml
# then
# convert to html
mjml %>% 
  mj_save_mjml() %>% 
  mj_convert_html("email.html")

# Or
# just save as html straight away
mjml %>% 
  mj_save("email.html")

# Or
# even easier
# send the email straight away
mjml %>% 
  mj_send() # fill in details
```

## Design

Basics of email design with `mjml`. 1) Put everything related to the document such as style and meta elements in `mj_head`. 2) Put everything related to the content of your email in `mj-body`. 3) In mjml, rows = `mj_section`. 4) Up to four `mj_columns`, specify width in percentage, i.e.: `width = 20%` (optional).

```{r, eval=FALSE}
mj_ml(
  mj_head(
    mj_font(
      href = "https://fonts.googleapis.com/css?family=Raleway",
      name = "Raleway"
    ),
    mj_preview("MJML Preview"), # email preview
    mj_title("MJML Title") # email title
  ),
  mj_body( # email content
    mj_section( # row 1
      mj_text("Some text")
    ),
    mj_section( # row 2
      mj_column(
        mj_carousel(
          mj_carousel_image(paste0("https://media.vanityfair.com/photos/",
                                   "54cbf3da998d4de83ba3602a/master/",
                                   "w_960,c_limit/image.jpg")),
          mj_carousel_image(paste0("https://media.vanityfair.com/photos/",
                                   "54cbf3dafde9250a6c402ed2/master/",
                                   "w_690,c_limit/image.jpg"))
        )
      )
    )
  )
) %>% 
  mj_save_mjml("email.html") %>% 
  mj_send_html(...)
```

### Templates

Use the Rstudio addins to insert email templates. Currently included templates: `Allura`, `Happy New Year`, `Card`, `Proof`.

Card Template below:

```{r, eval=FALSE}
  mj_ml(

    mj_head(
      mj_title("Say hello to card"),
      mj_font(
        name = "Roboto",
        href = "https://fonts.googleapis.com/css?family=Montserrat:300,400,500"
      ),
      mj_attributes(
        mj_all(`font-family` = "Montserrat, Helvetica, Arial, sans-serif"),
        mj_text(`font-weight` = "400", `font-size` = "16", color = "#000000", `line-height` = "24px"),
        mj_section(padding = 0)
      )
    ),

    mj_body(
      mj_container(
        `background-color` = "#F2F2F2",
        mj_section(
          padding = "10px 0 20px 0",
          mj_column(
            mj_text(
              align = "center",
              color = "#9B9B9B",
              `font-size` = "11px",
              "Writing A Good Headline For Your Advertisement"
            )
          )
        ),
        mj_section(
          padding = "20px 20px 0 20px",
          `background-color` = "#FFFFFF",
          mj_column(
            width = "35%",
            mj_text(
              align = "left",
              `font-size` = "20",
              `font-weight` = "500",
              "// BR&AND"
            )
          ),
          mj_column(
            width = "65%",
            mj_text(
              align = "right",
              `font-size` = "11",
              htmltools::a(
                href = "#",
                style = "color: #000000; text-decoration: none;",
                "HOME"
              ),
              "&nbsp;&nbsp;&nbsp;/&nbsp;&nbsp;&nbsp;",
              htmltools::a(
                href = "#",
                style = "color: #000000; text-decoration: none;",
                "SERVICE"
              ),
              "&nbsp;&nbsp;&nbsp;/&nbsp;&nbsp;&nbsp;",
              htmltools::a(
                href = "#",
                style = "color: #000000; text-decoration: none;",
                "THIRD"
              )
            )
          )
        ),
        mj_section(
          padding = "20px 20px 0 20px",
          `background-color` = "#FFFFFF",
          mj_column(
            mj_text(
              align = "center",
              `font-weight` = "300",
              padding = "30px 40px 10px 40px",
              `font-size` = "32px",
              `line-height` = "40x",
              color = "#5FA91D",
              "Free Advertising For Your Online Business."
            )
          )
        ),
        mj_section(
          padding = "10px 20px",
          `background-color` = "#FFFFFF",
          mj_column(
            mj_divider(width = "30px", `border-width` = "3px", `border-color` = "#9B9B9B")
          )
        ),
        mj_section(
          padding = "0 20px 20px 20px",
          `background-color` = "#FFFFFF",
          mj_column(
            width = "80%",
            mj_text(
              align = "center", `padding-top` = "10px", `font-weight` = "500", padding = "0",
              "A Right Media Mix Can Make The Difference."
            )
          )
        ),
        mj_section(
          `background-url` = "http://nimus.de/share/tpl-card/bg.jpg",
          `vertical-align` = "middle",
          `background-size` = "cover",
          `background-repeat` = "no-repeat",
          mj_column(
            width = "100%",
            mj_image(
              src = "http://nimus.de/share/tpl-card/lineshadow.png",
              alt = "",
              align = "center",
              border = "none",
              padding = "0"
            ),
            mj_text(
              align = "center", padding = "50px 40px 0 40px", `font-weight` = "300", padding = "0",
              paste("Marketers/advertisers usually focus their efforts on the people responsible for making the purchase.",
                    "In many cases, this is an effective approach but in other cases it can make for a totally useless",
                    "marketing campaign.")
            ),
            mj_button(
              align = "center",
              `background-color` = "#5FA91D",
              color = "#FFFFFF",
              `border-radius` = "2px",
              href = "#",
              `inner-padding` = "15px 30px",
              `padding-bottom` = "100",
              `padding-top` = "20",
              "CALL TO ACTION"
            )
          )
        ),
        mj_section(
          padding = "50px 0 0 0",
          `background-color` = "#FFFFFF",
          mj_column(
            mj_image(
              src = "http://nimus.de/share/tpl-card/bottom.png",
              alt = "bottom border",
              align = "center",
              border = "none",
              padding = "0"
            )
          )
        ),
        mj_section(
          padding = "10px 0 20px 0",
          mj_column(
            mj_text(
              align = "center",
              color = "#9B9B9B",
              `font-size` = "11px",
              htmltools::a(
                href = "#",
                style = "color: #9B9B9B;",
                "Unsubscribe"
              ),
              "from this newsletter",
              htmltools::br(),
              "52 Edison Court Suite 259 / East Aidabury / Cambodi",
              htmltools::br(),
              htmltools::a(
                href = "#",
                style = "color: #9B9B9B; text-decoration:none;",
                "Made by svenhaustein.de"
              )
            )
          )
        )
      )
    )
  )
```

<script async defer src="https://buttons.github.io/buttons.js"></script>
</div>
</main>
