---
title: "peity"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(peity)
library(htmltools)
```

`r peity(c(3,1,7,8), type = "donut")` `r peity(c(5,3,2,-1,-3,-2,2,3), type = "bar")` `r peity(c(0,-3,-6,-4,-5,-3,-5,-2), type = "bar")` `r peity(c(5,3,9,6,5,9,7,3), type = "line")` `r peity(c(5,2,3,1), type = "pie")` 

```{r intro}
div(class = "container-fluid",
    p(code("peity"), " is an htmlwidget for ", 
      a("Peity", href = "http://benpickles.github.io/peity/", target = "_blank"), 
      ": in-line charts", peity(c(1,5,2,6,5,3,1), type = "line"), "."),
    p(a(href="https://github.com/JohnCoene/peity", target = "_blank",
            HTML("<button class='bttn-unite bttn-lg bttn-danger'><i class='fa fa-github' aria-hidden='true'></i> Repository</button>"))))
```

[![Build Status](https://travis-ci.org/JohnCoene/peity.svg?branch=master)](https://travis-ci.org/JohnCoene/peity)
[![saythanks](https://img.shields.io/badge/say-thanks-ff69b4.svg)](https://saythanks.io/to/JohnCoene)

```{r install head}
div(class = "page-header",
    h2("Install"))
```

```{r install code, eval=FALSE, echo=TRUE}
devtools::install_github("JohnCoene/peity")
```

```{r examples head}
div(class = "page-header",
    h2("Examples"))
fun <- htmlwidgets::JS('function(_, i, all) {
    var g = parseInt((i / all.length) * 255)
    return "rgb(255, " + g + ", 0)"
  }')

fun2 <- htmlwidgets::JS('function(_, i, all) {
    var g = parseInt((i / all.length) * 255)
    return "rgb(255, " + g + ", 0)"
  }')
```

Reproducing examples from the [official documentation](http://benpickles.github.io/peity/):

1. `r peity(c(5,3,9,6,5,9,7,3,5,2), type = "bar", options = list(fill = c("red", "green", "blue")))`
2. `r peity(c(5,3,2,-1,-3,-2,2,3,5,2), type = "bar", options = list(fill = htmlwidgets::JS("function(value) {return value > 0 ? 'green':'red'}")))`
3. `r peity(c(0,-3,-6,-4,-5,-4,-7,-3,-5,-2), type = "bar", options = list(fill = fun))`
4. `r peity(c(4,7,6,5), type = "pie", options = list(fill = c("cyan", "magenta", "yellow", "black")))`
5. `r peity(c(5,3,9,6,5), type = "pie", options = list(fill = fun2))`

```{r, echo=TRUE, eval=FALSE}
# 1
peity(c(5,3,9,6,5,9,7,3,5,2), type = "bar", options = list(fill = c("red", "green", "blue")))

# 2
peity(c(5,3,2,-1,-3,-2,2,3,5,2), type = "bar", options = list(fill = htmlwidgets::JS("function(value) {
                                                                                     return value > 0 ? 'green':'red'}")))

# 3
fun <- htmlwidgets::JS('function(_, i, all) {
    var g = parseInt((i / all.length) * 255)
    return "rgb(255, " + g + ", 0)"
  }')
peity(c(0,-3,-6,-4,-5,-4,-7,-3,-5,-2), type = "bar", options = list(fill = fun))

# 4
peity(c(4,7,6,5), type = "pie", options = list(fill = c("cyan", "magenta", "yellow", "black")))

# 5
fun2 <- htmlwidgets::JS('function(_, i, all) {
    var g = parseInt((i / all.length) * 255)
    return "rgb(255, " + g + ", 0)"
  }')
peity(c(5,3,9,6,5), type = "pie", options = list(fill = fun2))
```