---
title: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(htmltools)
```

<main>
<div class = "container">

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/reporter.svg?branch=master)](https://travis-ci.org/JohnCoene/reporter)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/JohnCoene/reporter?branch=master&svg=true)](https://ci.appveyor.com/project/JohnCoene/reporter)

```{r}
tags$img(
  src = "img/fullpage_devices.png",
  class = "responsive-img"
)
```

`reporter` is a set of Rmarkdown formats currently including:

* fullpage - Not into slides? Me neither! This comes close enough.
* material (WIP)

I implemented fullpage.js because I actually despise slides, it's the most misused form of reporting; it should only be used for actual presentation in my opinion. However the management loves it so I have to comply. Until I stumbled upon [fullpage.js](https://alvarotrigo.com/fullPage/) which is a neat hybrid of long-form and slide formats.

`r br()`

```{r}
p(a(href = "https://github.com/JohnCoene/reporter", 
    target = "_blank",
    class = "btn blue",
    "Repository"))
```

```{r install head}
div(class = "page-header",
    h2("Install"))
```

```{r install code, eval=FALSE, echo=TRUE}
devtools::install_github("JohnCoene/reporter")
```

```{r}
p(a(href = "fullpage_demo", 
    target = "_blank",
    class = "btn blue lighten-1",
    "Demo"))
```

```{r}
div(class = "page-header",
    h2("Full page"))
```

```{r}
tags$ul(
  class = "collection with-header",
  tags$li(
    class = "collection-header",
    h4(
      "Featrures"
    )
  ),
  tags$li(
    class = "collection-item",
    "Slides"
  ),
  tags$li(
    class = "collection-item",
    "Background color"
  ),
  tags$li(
    class = "collection-item",
    "Navigation"
  ),
  tags$li(
    class = "collection-item",
    "And more..."
  )
)
```

```{r}
tags$ul(
  class = "collection with-header",
  tags$li(
    class = "collection-header",
    h4(
      "Options"
    )
  ),
  tags$li(
    class = "collection-item",
    "toc: Table of content as menu, i.e.:",
    code("toc: true")
  ),
  tags$li(
    class = "collection-item",
    "background: background color of sections, see demo."
  ),
  tags$li(
    class = "collection-item",
    "continuousVertical"
  ),
  tags$li(
    class = "collection-item",
    "continuousHorizontal"
  ),
  tags$li(
    class = "collection-item",
    "navigation: whether to show navigation"
  ),
  tags$li(
    class = "collection-item",
    "navigationPosition: position of aforementioned",
    code("navigation")
  ),
  tags$li(
    class = "collection-item",
    "slidesNavigation"
  )
)
```

</div>
</main>