---
title: "reporter"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(htmltools)
```

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/reporter.svg?branch=master)](https://travis-ci.org/JohnCoene/reporter)

`reporter` is a set of Rmarkdown formats currently including:

* fullpage - Not into slides? Me neither! This comes close enough.
* material (WIP)

`r br()`

```{r}
p(a(href="https://github.com/JohnCoene/reporter", target = "_blank",
            HTML("<button class='bttn-unite bttn-lg bttn-danger'><i class='fa fa-github' aria-hidden='true'></i> Repository</button>")))
```

```{r install head}
div(class = "page-header",
    h2("Install"))
```

```{r install code, eval=FALSE, echo=TRUE}
devtools::install_github("JohnCoene/reporter")
```

```{r examples head}
div(class = "page-header",
    h2("Demos"))
```

```{r}
p(a(href="fullpage_demo", target = "_blank",
            HTML("<button class='bttn-unite bttn-lg bttn-info'><i class='fa fa-file-text' aria-hidden='true'></i> Full Page</button>")))
```

```{r}
div(class = "page-header",
    h2("Full page"))
```

Features:

- slides
- background colors
- navigation
- table of content
- and more

Options:

- `toc` - Table of content as menu, i.e.: `toc: true`
- `background` - background color of sections, i.e.:
```
- background:
    - blue
    - red
    - green
```
- `continousVertical`
- `continuousHorizontal`
- `navigation` whether to show navigation
- `navigationPosition` position of aforementioned `navigation`
- `slidesNavigation`