---
title: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(htmltools)
library(bibler)
library(uvcharts)
data("king_james_df")
```

<main>
<div class = "container">

```{r}
h1(
  "bibler"
)
```

```{r chart header}
# base Bing Liu lexicons
neg <- readLines("negative-words.txt")
neg <- neg[36:length(neg)]
pos <- readLines("positive-words.txt")
pos <- pos[36:length(pos)]

data("middle_english_negative")
data("middle_english_positive")
pos <- c(pos, middle_english_positive)
neg <- c(neg, middle_english_negative)

# sentiment scoring FUN
sentiment_score = function(text, pos.words, neg.words){
  scores = plyr::laply(text,
                 function(text, pos.words, neg.words){
                   text = gsub("[[:punct:]]", "", text)
                   text = gsub("[[:cntrl:]]", "", text)
                   text = gsub('\\d+', '', text)
                   text = sapply(text, tolower)
                   word_list = stringr::str_split(text, "\\s+")
                   words = unlist(word_list)
                   positive_matches = match(words, pos.words)
                   negative_matches = match(words, neg.words)
                   positive_matches = !is.na(positive_matches)
                   negative_matches = !is.na(negative_matches)
                   score = sum(positive_matches) - sum(negative_matches)
                   return(score)
                 }, pos.words, neg.words)
  return(scores)
}

# score each verse
king_james_df$Sentiment <- sentiment_score(king_james_df$Text, pos, neg)

# mean sentiment / book
bks <- plyr::ddply(king_james_df, c("King.James.Bible", "Book.Number"),
                                    plyr::summarise, Sentiment = mean(Sentiment))

# bks$colour <- ifelse(bks$Sentiment >= 0, "#59922b", "#f05b4f")
bks$label <- ifelse(bks$Sentiment >= 0, "positive", "negative")

bks %>% 
  group_by(label) %>% 
  uv_bar(Book.Number) %>% 
  uv_add(Sentiment) %>% 
  uv_graph(custom.palette = c("red", "green"), orientation = "Vertical") %>% 
  uv_baropt(fontsize = 0) %>% 
  uv_label(fontsize = 5, strokecolor = "grey") %>% 
  uv_axis(showsubticks = FALSE, opacity = 0.2, strokecolor = "#d3d3d3") %>% 
  uv_meta(caption = "King James Bible", subcaption = "Sentiment Analysis", hlabel = "Book Number", vlabel = "Sentiment Score") %>% 
  uv_frame(bgcolor = "none") %>% 
  uv_legend(position = "right")
```

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/bibler.svg?branch=master)](https://travis-ci.org/JohnCoene/bibler) [![Build status](https://ci.appveyor.com/api/projects/status/fgqivf16f1u7jrug/branch/master?svg=true)](https://ci.appveyor.com/project/JohnCoene/bibler/branch/master)
[![saythanks](https://img.shields.io/badge/say-thanks-ff69b4.svg)](https://saythanks.io/to/JohnCoene)

```{r title}
h3("Install")
```

```{r install code, echo=TRUE, eval=FALSE}
devtools::install_github("JohnCoene/bibler")
```

```{r}
h3("Datasets")
```

1. `king_james_df` The King James Bible as data.frame
2. `king_james_tm` The King James Bible as [tm](https://cran.r-project.org/package=tm) corpus (`c("VCorpus", "Corpus"`)
3. `king_james_books` List of books that constitute the King James Bible
4. `apocrypha_df` The Apocrypha as data.frame
5. `apocrypha_tm` The Apocrypha as [tm](https://cran.r-project.org/package=tm) corpus (`c("VCorpus", "Corpus"`)
6. `apocrypha_books` List of books that constitute the Apocrypha
7. `middle_english_stopwords` Character vector of Middle English stopwords
8. `middle_english_positive` Lexicon of positive Middle English terms
9. `middle_english_negative` Lexicon of negative Middle English terms

See [vignette](packages/bibler/examples.html) for more details.

</div>
</main>