---
title: "Docs"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# uvcharts-shiny

Output and render functions for using uvcharts within Shiny applications and interactive Rmd documents.

## Arguments

* `outputId` output variable to read from
* `width`, `height` Must be a valid CSS unit (like '100%', '400px', 'auto') or a number, which will be coerced to a string and have 'px' appended.
* `expr` An expression that generates a uvcharts
* `env` The environment in which to evaluate expr.
* `quoted` Is expr a quoted expression (with quote())? This is useful if you want to save an expression in a variable.

# uv_add

Add a serie to plot

## Arguments

* p a `uvcharts` object.
* `serie` values to plot.

## Examples

```{r}
mtcars %>%
  uv_bar(mpg) %>%
  uv_add(qsec) %>%
  uv_add(drat)
```

# uv_areaopt

Customise the properties specific to area chart.

## Arguments

* `p` a `uvcharts` object.
* `interpolation` line interpolation. Defaults to linear see details for valid values.
* `opacity` oOpacity in the case of simple Area chart, defaults to 0.2.
* `offset` offset, defaults to zero. See details for valid values.

## Details

Valid values for interpolation argument:

* `linear`
* `basis`
* `cardinal`
* `monotone`

Valid values for offset argument:

* `zero`
* `wiggle`
* `silhouette`
* `expand`

## Examples

```{r}
mtcars %>%
  uv_area(qsec) %>%
  uv_add(mpg) %>%
  uv_areaopt(opacity = 0.9)
```

# uv_axis

Customise the chart axis.

## Arguments

* `p` a `uvcharts` object.
* `opacity` opacity of the axis lines drawn for reference, defaults to `1`.
* `ticks` number of major ticks on the measure axis.
* `subticks` number of minor ticks on the measure axis.
* `padding` any CSS size.
* `minor` length of the minor ticks towards the label.
* `strokecolor` color of axis lines, any Color Code or Color String or `none`. Defaults to `#000000`.
* `fontfamily` any font, defaults to `Arial`.
* `fontsize` font size. Defaults to `11`.
* `fontweight` font weight, defaults to `bold`.
* `showticks` show ticks flag, `TRUE` or `FALSE`, defaults to the former.
* `showsubticks` show subticks flag, `TRUE` or `FALSE`, defaults to the former.
* `showtext` show text flag, `TRUE` or `FALSE`, defaults to the former.

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_axis(opacity = 0.6, ticks = 10, strokecolor = "blue", showtext = FALSE)
```

# uv_baropt

Customise the chart bars.

## Arguments

* `p` a `uvcharts` object.
* `strokecolor` any Color Code or Color String or none. defaults to `#000000`.
* `fontsize` font size. Defaults to `11`.
* `fontweight` font weight, defaults to `bold`.
* `fontfamily` any font, defaults to `Arial`.
* `textcolor` text color used for the numbers, defaults to `#000000`.

## Examples

```{r}
mtcars %>%
  uv_stackbar(qsec) %>%
  uv_add(mpg) %>%
  uv_add(drat) %>%
  uv_baropt(fontsize = 7)
```

# uv_caption

Customise the chart caption.
Customise the chart subcaption.

## Usage

`uv_caption(p, fontfamily, fontsize, fontweight, textdecoration, strokecolor, cursor)`
`uv_subcaption(p, fontfamily, fontsize, fontweight, textdecoration, strokecolor, cursor)`

## Arguments

* `p` a `uvcharts` object.
* `fontfamily` any font, defaults to `Arial`.
* `fontsize` font size. Defaults to `11`.
* `fontweight` font weight, defaults to bold.
* `textdecoration` text decoration applied on the caption, defaults to `none`.
* `strokecolor` any Color Code or Color String or none. defaults to `#000000`.
* `cursor` precision on the labels in case of decimal values. Defaults to `pointer`.

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_meta("Title") %>%
  uv_caption(fontsize = 30)
```

# uv_charts

Initiate a uvchart

## Usage

`uv_charts(data, x, type = "Line", width = "100%", height = "100%", elementId = NULL)`
`uv_bar(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_line(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_area(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_stackbar(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_stackarea(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_pie(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_donut(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_percentbar(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_percentarea(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_stepupbar(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_polar(data, x, width = "100%", height = "100%", elementId = NULL)`
`uv_waterfall(data, x, width = "100%", height = "100%", elementId = NULL)`

## Arguments

* `data` data.frame of data to plot.
* `x` x variable.
* `type` type of chart to plot, see details.
* `width`, `height` Must be a valid CSS unit (like '100%', '400px', 'auto') or a number, which will be coerced to a string and have 'px' appended.
* `elementId` id of div element containing chart.

## Examples

```{r}
mtcars %>%
  uv_charts(mpg, type = "Area") %>%
  uv_add(qsec)

mtcars %>%
  uv_bar(mpg) %>%
  uv_add(qsec)

mtcars %>%
  uv_line(mpg) %>%
  uv_add(qsec)

mtcars %>%
  uv_pie(mpg) %>%
  uv_add(qsec)

mtcars %>%
  uv_stackbar(mpg) %>%
  uv_add(qsec)

mtcars %>%
  uv_percentarea(mpg) %>%
  uv_add(qsec)

p <- uv_line(mtcars, qsec)
p <- uv_add(p, mpg)
p
```

# uv_config

Configure the chart.

## Arguments

* `p` a uvcharts object.
* `...` any argument to pass to config.

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_config(legend = list(showlegends = FALSE))
```

# uv_dimension

Customise the chart dimensions.

## Arguments

* `p` a `uvcharts` object.
* `width`, `height` any CSS size.
* `override` if `TRUE`, overrides the div’s `height` and `width`, recommended.

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_dimension(width = 200)
```

# uv_frame

Customise the chart frame.

## Arguments

* `p` a uvcharts object.
* `bgcolor` any Color Code or Color String or `none`.

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_frame(bgcolor = "black")
```

# uv_graph

Customise the graph object.

## Arguments

* `p` a `uvcharts` object.
* `palette` palette name, see details for valid values. Defaults to Brink.
* `bgcolor` background color used for the entire chart include the margin spaces.
* `orientation` orientation of the chart for a different layout based on requirements. Can take `Horizontal` or `Vertical`, defaults to the former.
* `custom.palette` override the palette with your own color palette by providing a non empty list of color codes. They are used in order for corresponding serie (`uv_add`). Pass colors as `list`.
* `opacity` opacity of the entire chart to make it blend into any background of your choice. Defaults to `1`.
* `responsive` `TRUE` for responsive sizing (default).

## Details

Valid values for palette argument.

* `Plain`
* `Simple`
* `Olive`
* `Candid`
* `Sulphide`
* `Soft`
* `Lint`

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_graph(palette = "Plain")
```

# uv_label

Customise the chart labels.

## Arguments

* `p` a `uvcharts` object.
* `fontfamily` any font, defaults to `Arial`.
* `fontsize` font size. Defaults to `11`.
* `fontweight` font weight, defaults to `bold`.
* `strokecolor` any Color Code or Color String or none. defaults to `#000000`.
* `showlabel` show labels flag, `TRUE` or `FALSE`, defaults to the former.
* `precision` precision on the labels in case of decimal values. Defaults to `2`.
* `prefix` any prefix which needs to be added to the label.
* `suffix` any suffix which needs to be added to the label.

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_label(fontsize = 6, strokecolor = "red")
```

# uv_legend

Configure the legend.

## Arguments

* `p` a `uvcharts` object.
* `showlegends` boolean.
* `position` legend position, i.e.: `right`.

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_legend(position = "right")
```

# uv_lineopt

Customise the properties affecting Line chart.

## Arguments

* `p` a `uvcharts` object.
* `interpolation` line interpolation. Defaults to linear see details for valid values.

## Details

Valid values for `interpolation` argument:

* `linear`
* `basis`
* `cardinal`
* `monotone`

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_lineopt(interpolation = "cardinal")
```

# uv_margin

Customise the chart margin.

## Arguments

* `p` a `uvcharts` object.
* `top`, `bottom`, `left`, `right` any CSS size.

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_meta("Title", "Subtitle", "x axis", "y axis")
```

# uv_pieopt

Customise the properties specific to Pie Chart.
Customise the properties specific to Donut Chart.

## Usage

`uv_pieopt(p, fontfamily, fontsize, fontweight, fontvariant, fontfill, strokecolor, strokewidth)`
`uv_donutopt(p, fontfamily, fontsize, fontweight, fontvariant, fontfill, strokecolor, strokewidth, factor)`

## Arguments

* `p` a `uvcharts` object.
* `fontfamily` any font, defaults to `Arial`.
* `fontsize` font size. Defaults to `11`.
* `fontweight` font weight, defaults to `bold`.
* `fontvariant` font variant used on the text, defaults to `small-caps`, can also take normal.
* `fontfill` text color on the measure, defaults to `#000000`.
* `strokecolor` any Color Code or Color String or none. defaults to `#000000`.

## Examples

```{r}
mtcars %>%
  uv_pie(qsec) %>%
  uv_add(mpg) %>%
  uv_pieopt(fontfill = "white")
```

# uv_scale

Customise the chart scale.

## Arguments

* `p` a `uvcharts` object.
* `type` scale used to represent values on the chart, see details for valid values.
* `ordinality` defines the gap between 2 consecutive labels, defaults to `0.2`.

## Details

Valid values for type argument, defaults to linear:

* `linear`
* `log`
* `pow`
* `sqrt`

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_scale(type = "log")
```

# uv_tooltip

Customise the chart tooltip.

## Arguments

* `p` a `uvcharts` object.
* `show` flag to enable or disable tooltip functionality, defaults to `TRUE`.
* `format` defines custom format for tooltip, character string. defaults to` %c [%l] : %v`

## Examples

```{r}
mtcars %>%
  uv_charts(qsec) %>%
  uv_add(mpg) %>%
  uv_tooltip(format = "%v")
```