---
title: ""
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<main>
<div class = "container">

```{r, echo=FALSE, eval=TRUE}
h1(
  "Options"
)
```

## Functions

There are four functions that allow you to customise charts' series:

1. `opt_ist`
2. `lineopt_ist`
3. `baropt_ist` 
4. `pieopt_ist`

You can pass any otpion for any series `type` with `opt_ist`. However for the sake of convenience and clarity, there are also type-specific option functions.

## Missing Data

```{r}
set.seed(19880525) # create missing data
df <- data.frame(x = 1:20, 
                 y = sample(c(round(runif(20, 10, 20)), rep(NA, 8)), 20),
                 z = sample(c(round(runif(20, 10, 20)), rep(NA, 8)), 20))
```

### Holes

```{r}
df %>%
  chart_ist(x) %>%
  add_ist(y) %>%
  add_ist(z) %>% # leave holes (NA)
  yaxis_ist(onlyInteger = TRUE)
```

### Fill holes

```{r}
df %>%
  chart_ist(x) %>%
  add_ist(y) %>%
  add_ist(z) %>% 
  lineopt_ist(fillHoles = TRUE) %>%
  yaxis_ist(onlyInteger = TRUE)
```

## Series

Set options to specific series by refering to their `name`.

```{r}
mtcars$models <- row.names(mtcars)
mtcars[1:15,] %>%
  chart_ist(models) %>%
  add_ist(cyl, name = "serie-1") %>%
  add_ist(drat, name = "serie-2") %>%
  add_ist(wt, "serie-3") %>%
  lineopt_ist(name = "serie-1", lineSmoothing = "step") %>%
  lineopt_ist(name = "serie-2", showArea = TRUE, showPoint = FALSE) %>%
  lineopt_ist(name = "serie-3", lineSmoothing = 3, showPoint = TRUE)
```

## Distributed data

set `distributeSeries` to `TRUE` for categorical data.

```{r}
mtcars[1:10,] %>%
  chart_ist(x = models, type = "bar") %>%
  add_ist(disp) %>%
  baropt_ist(distributeSeries = TRUE)
```

## Grid & Axis

Customise the grid and axis.

```{r}
mtcars[1:15,] %>%
  chart_ist(x = models, type = "bar") %>%
  add_ist(disp) %>%
  yaxis_ist(position = "end", prefix = "$", suffix = "M", showGrid = TRUE) %>%
  xaxis_ist(position = "end", showGrid = FALSE)
```

</div>
</main>