---
title: "Bar charts"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(echarts)
```

## Marks

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/bar1.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame(x = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
                 y = c(2.0, 4.9, 7.0, 23.2, 25.6, 76.7, 135.6, 162.2, 32.6, 20.0, 6.4, 3.3),
                 z = c(2.6, 5.9, 9.0, 26.4, 28.7, 70.7, 175.6, 182.2, 48.7, 18.8, 6.0, 2.3))

avg <- list(list(type = "average", name = "average"))
point <- list(list(type = "max", name = "maximum"))

df %>% 
  echart(x, width = "100%") %>% 
  ebar(y, name = "evaporation") %>% 
  ebar(z, name = "precipitation") %>% 
  emark_line("all", data = avg) %>% 
  emark_point("all", data = point) %>% 
  elegend() %>% 
  etheme("macarons") %>% 
  etoolbox_magic(type = list("line", "bar", "stack", "tiled")) %>% 
  etitle("Evaporation and precipitation")
```

# Stacked bars

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/bar2.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame(x = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
                 radio = c(320, 332, 301, 334, 390, 330, 320),
                 social = c(120, 132, 101, 134, 90, 230, 210),
                 video = c(220, 182, 191, 234, 290, 330, 310),
                 SEM = c(150, 232, 201, 154, 190, 330, 410),
                 organic = c(862, 1018, 964, 1026, 1679, 1600, 1570)) 

line <- list(
  normal = list(
    lineStyle = list(
      type = "dashed"
    )
  ))

df %>% 
  echart(x, width = "100%") %>% 
  ebar(radio, stack = "grp") %>% 
  ebar(social, stack = "grp") %>% 
  ebar(video, stack = "grp") %>% 
  ebar(SEM, barWidth = 5) %>% 
  ebar(organic) %>% 
  emark_line(itemStyle = line, data = list(list(type = "max"))) %>% 
  etooltip(axisPointer = list(type = "shadow"))
```

# Waterfall

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/bar7.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame(x = c("Total", "Rent", "Utilities", "Transport", "Food costs", "Misc"),
                 hidden = c(0, 1700, 1400, 1200, 300, 0),
                 values = c(2900, 1200, 300, 200, 900, 300))

hide_bars <- list(
  normal = list(
    barBorderColor = "rgba(0,0,0,0)",
    color = "rgba(0,0,0,0)"),
  emphasis = list(
    barBorderColor = "rgba(0,0,0,0)",
    color = "rgba(0,0,0,0)")
  )

inside_label <- list(normal = list(label = list(show = TRUE, position = "inside")))

df %>% 
  echart(x, width = "100%") %>% 
  ebar(hidden, itemStyle = hide_bars, stack = "stack") %>% 
  ebar(values, stack = "stack", itemStyle = inside_label) %>% 
  etheme("macarons") %>% 
  etooltip(axisPointer = list(type = "shadow")) %>% 
  etitle("Shenzhen minimum living expenses (RMB)", subtext = "From ExcelHome", sublink = "http://e.weibo.com/1341556070/AjQH99che")
```

# Thermometer

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/bar10.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame(x = c('Cosco','CMA','APL','OOCL','Wanhai','Zim'),
                 y = c(260, 200, 220, 120, 100, 80),
                 z = c(40, 80, 50, 80,80, 70))

item1 <- list(normal = list(
  color = "tomato",
  barBorderColor = 'tomato',
  barBorderWidth = 6,
  barBorderWidth = 0,
  label = list(
    show = TRUE,
    positon = "insideTop"
  )
))

item2 <- list(normal = list(
  color = "#FFF",
  barBorderColor = 'tomato',
  barBorderWidth = 6,
  barBorderWidth = 0,
  label = list(
    show = TRUE,
    positon = "top",
    textStyle = list(color = "tomato")
  )
))

df %>% 
  echart(x, width = "100%") %>% 
  ebar(y, stack = "grp", itemStyle = item1, barCategoryGap = '50%') %>% 
  ebar(z, stack = "grp", itemStyle = item2) %>% 
  etoolbox_full() %>% 
  etitle("Thermometer chart", subtext = "From ExcelHome", sublink = "http://e.weibo.com/1341556070/AizJXrAEa")
```