---
title: "Line chart examples"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(echarts)
```

# Mark points & lines

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/line2.html#-en) taken from Baidu's EChart official website.

```{r mark point}
df <- data.frame(x = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
                 y = c(11, 11, 15, 13, 12, 13, 10),
                 z = c(1, -2, 2, 5, 3, 2, 0))

point <- list(
  list(type = "max", name = "maximum"), 
  list(type = "min", name = "minimum"))

avg <- list(list(type = "average", name = "average"))

df %>% 
  echart(x) %>% 
  eline(y, smooth = TRUE, name = "serie 1") %>% 
  eline(z, smooth = TRUE, name = "serie 2") %>% 
  emark_point("all", data = point) %>% 
  emark_line("all", data = avg) %>% 
  etooltip() %>% 
  elegend() %>% 
  exAxis_category(boundaryGap = FALSE) %>% 
  etoolbox_magic(type = list("line", "bar")) %>% 
  etitle(text = "Temperature", subtext = "Fake data")
```

# Stacked lines

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/line2.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame(x = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
                 y = c(120, 132, 101, 134, 90, 230, 210),
                 z = c(220, 182, 191, 234, 290, 330, 310),
                 w = c(150, 232, 201, 154, 190, 330, 410)) 

df %>% 
  echart(x) %>% 
  eline(y, name = "Y") %>% 
  eline(z, stack = "grp1", name = "Z") %>% 
  eline(w, stack = "grp1", name = "W") %>% 
  elegend() %>% 
  etoolbox() %>% 
  etoolbox_magic(type = list('line', 'bar', 'stack', 'tiled'))
```

# Basic Area

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/line3.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame(x = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
                 y = c(10, 12, 21, 54, 260, 830, 710),
                 z = c(30, 182, 434, 791, 390, 30, 10),
                 w = c(1320, 1132, 601, 234, 120, 90, 20))

df %>% 
  echart(x) %>% 
  earea(y, smooth = TRUE) %>% 
  earea(z, smooth = TRUE) %>% 
  earea(w, smooth = TRUE) %>% 
  exAxis_category(boundaryGap = FALSE) %>% 
  etheme("macarons") %>% 
  etooltip() %>% 
  etoolbox_magic(type = list('line', 'bar', 'stack', 'tiled')) %>% 
  etoolbox_mark() %>% 
  etoolbox_restore() %>% 
  etoolbox_save()
```

# Stacked Area

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/line4.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame(x = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
                 y = c(120, 132, 101, 134, 90, 230, 210),
                 z = c(220, 182, 191, 234, 290, 330, 310),
                 w = c(150, 232, 201, 154, 190, 330, 410))

df %>% 
  echart(x) %>% 
  earea(y, smooth = TRUE, stack = "grp") %>% # stack
  earea(z, smooth = TRUE, stack = "grp") %>% # stack
  earea(w, smooth = TRUE) %>% # not stacked
  exAxis_category(boundaryGap = FALSE) %>% 
  etheme("macarons") %>% 
  etooltip()
```

# Irregular line

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/line8.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame()
for(i in seq(1:100)){
  date <- Sys.time() + i * 3600
  value <- round(runif(1, 5, 20))
  df <- rbind.data.frame(df, cbind.data.frame(date, value))
}

df %>% 
  echart(date) %>% 
  eline(value, symbolSize = htmlwidgets::JS("function(value){ return value/2}"), showAllSymbol = TRUE) %>% 
  etheme("macarons") %>% 
  ezoom()
```

# Multiple axis

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/line6.html#-en) taken from Baidu's EChart official website.

```{r}
df <- data.frame()
for(i in seq(1:100)){
  date <- Sys.time() + i * 3600
  y <- round(runif(1, 1, 5))
  z <- runif(1, -4, -1)
  df <- rbind.data.frame(df, cbind.data.frame(date, y, z))
}

df %>% 
  echart(date) %>% 
  earea(y, smooth = TRUE) %>% 
  earea(z, smooth = TRUE, yAxisIndex = 1) %>% 
  eyAxis_value(name = "y", max = 15) %>% 
  eyAxis_value(name = "z", append = TRUE, min = -5) %>% 
  ezoom() %>% 
  etheme("macarons")
```