---
title: "maps"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(echarts)
```

# Maps

## How it works

Some things remain unchanged; you still `%>%` your data and initiate the chart with the `echart` function. Once this done you can setup a map with `emap` and `emap_` and pass arguments that will apply to the map as a whole. Following that you add, if necessary, coordinates of points with `emap_coords` and `emap_coords`. Note that this does NOT draw points on the map, this is merely a reference table for your actual series to plot, i.e.: `points` or `lines`. Adding coordinates is obviously not required for choropleth maps (`emap_choropleth` and `emap_choropleth_`).

## Examples

Following is a reproduction examples from [plotly](https://plot.ly/r/lines-on-maps/) using their datasets:

* [airports](https://raw.githubusercontent.com/plotly/datasets/master/2011_february_us_airport_traffic.csv')
* [flights](https://raw.githubusercontent.com/plotly/datasets/master/2011_february_aa_flight_paths.csv)

The datasets above are downloaded from R:

```{r dl}
air <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2011_february_us_airport_traffic.csv')
flights <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2011_february_aa_flight_paths.csv')
```

Inspect the datasets yourself to understand the following examples, `str(air)` & `str(flights)`.

## Points basic

Here I simply plot the location of airports.

```{r}
air %>% 
  echart(iata, width = "100%") %>% # x here corresponds to the name of each coordinate
  emap() %>% # setup map
  emap_coords(long, lat) %>% # actual coordinates
  emap_points(cnt, symbolSize = 2) # value corresponding to each coordinate
```

## Points groups

We can group the airports by `state` to have one serie and color for each, select the map of the United States only and change the symbol.

```{r}
air %>% 
  group_by(state) %>% 
  echart(iata, width = "100%") %>% 
  emap_(mapType = "world|United States of America") %>% 
  emap_coords(long, lat) %>% 
  emap_points(cnt, symbol = "star", symbolSize = 10) 
```

## Point size

Using a bit of JS we can set the symbol size to that of value we pass, `cnt`.

```{r}
sizeFUN <- htmlwidgets::JS(" function (v){ return v/1000 }")

air %>% 
  group_by(state) %>% 
  echart(iata, width = "100%") %>% 
  emap(mapType = "world|United States of America") %>% 
  emap_coords(long, lat) %>% 
  emap_points(cnt, symbol = "circle", symbolSize = sizeFUN) 
```

## Lines

ECharts also lets you plot line on maps.  

```{r}
air %>% 
  echart(iata, width = "100%") %>% 
  emap(mapType = "world|United States of America") %>% 
  emap_coords(long, lat) %>% 
  emap_lines(flights, airport1, airport2) %>% 
  emap(mapType = "world|United States of America") 
```

It may be confusing at first but ECharts has you, first, pass the *named* coordinates of the points then the edges as *name of source* to *name of target*. Hence passing the coordinates named `iata` (x in `echart` function) then passing edges as `airport1` to `airport2`.

## Combine

You can combine points and lines.

```{r}
air %>% 
  echart(iata, width = "100%") %>% 
  emap(mapType = "world|United States of America") %>% 
  emap_coords(long, lat) %>% 
  emap_points(cnt, symbolSize = sizeFUN, symbol = "circle") %>% 
  emap_lines(flights, airport1, airport2)
```

## Combine groups

Remember we grouped the data by `state` earlier on, we can do the same here. We will also group the edges by states so `echarts` will match our edges to our points.

Below I merge the edges (`flights`) with the airports (`air`) by airport of arrival (`airport2`), then simply group the edges by `state`.

```{r}
# merge flights with air to get state of departure
flights <- dplyr::left_join(flights, air, by = c("airport2" = "iata"))
flights <- flights[complete.cases(flights),] # remove NAs

# group flights like air
flights <- flights %>% 
  group_by(state)

air %>% 
  group_by(state) %>% 
  echart(iata, width = "100%") %>% 
  emap(mapType = "world|United States of America") %>% 
  emap_coords(long, lat) %>% 
  emap_points(cnt, symbol = "circle", symbolSize = sizeFUN) %>% 
  emap_lines(flights, airport1, airport2)
```

## Beautify

Finally you can beautify the map

```{r}
# options to set map backgroudn to dark
dark <- list(normal = list(borderColor = "rgba(100,149,237,1)",
                           borderWidth = 0.5,
                           areaStyle = list(color = '#1b1b1b')))

# customise line effect
line.effect <- list(loop = TRUE,
                    show = TRUE,
                    scaleSize = 1,
                    period = 40,
                    shadowBlur = 5)

air %>% 
  group_by(state) %>% 
  echart(iata, width = "100%") %>% 
  emap(mapType = "world|United States of America", 
       itemStyle = dark) %>% 
  emap_coords(long, lat) %>% 
  emap_points(cnt,
              symbol = "emptyCircle", 
              effect = list(show = TRUE, shadowBlur = 10),
              symbolSize = sizeFUN) %>% 
  emap_lines(flights, airport1, airport2, 
             effect = line.effect) %>% 
  etheme("dark")
```
