---
title: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(echarts)
```

<main>
<div class = "container">

```{r, echo=FALSE}
h1(
  "Pie charts"
)
```

### Basic pie

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/pie1.html#-en) taken from Baidu's EChart official website.

```{r pie basic}
pie <- data.frame(slices = c('Direct access', 'mail marketing', 'affiliate ad', 'video ad', 'search engine'),
                  values = c(335, 310, 234, 135, 1548))

# funnel options
opts <- list(funnel = list(x = "25%",
                           width = "50%",
                           funnelAlign = "left",
                           max = 1548))

pie %>% 
  echart(slices, width = "100%") %>% 
  epie(values) %>% 
  elegend(orient = "vertical", x = "left", radius = "55%") %>% 
  etoolbox_full() %>% 
  etoolbox_magic(type = list("pie", "funnel"), option = opts) %>% 
  etheme("macarons") %>% 
  etooltip(trigger = "item") %>% 
  etitle("User access", "Fake data", x = "center")
```

### Doughnut

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/pie2.html#-en) taken from Baidu's EChart official website.

```{r doughnut}
pie <- data.frame(slices = c('Direct access', 'mail marketing', 'affiliate ad', 'video ad', 'search engine'),
                  values = c(335, 310, 234, 135, 1548))

# funnel options
opts <- list(funnel = list(x = "25%",
                           width = "50%",
                           funnelAlign = "center",
                           max = 1548))

# doughnut inside label
lab <- list(
  normal = list(label = list(show = FALSE), # hide normal labels
                labelLine = list(show = FALSE)), # hide label lines
  emphasis = list(label = list(show = TRUE, position = "center", # place on-hover labels inside doughnut 
                               textStyle = list(fontSize = 20, fontWeight = "bold")))) # customise font of inside label

pie %>% 
  echart(slices, width = "100%") %>% 
  epie(values, radius = list("55%", "70%"), itemStyle = lab) %>% 
  elegend(orient = "vertical", x = "left", radius = "55%") %>% 
  etoolbox_full() %>% 
  etoolbox_magic(type = list("pie", "funnel"), option = opts) %>% 
  etheme("macarons")%>% 
  etooltip(trigger = "item")
```

### Rose diagram

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/pie4.html#-en) taken from Baidu's EChart official website.

```{r rose}
pie <- data.frame(slices = c('Direct access', 'mail marketing', 'affiliate ad', 'video ad', 'search engine'),
                  values = c(335, 310, 234, 135, 500))

# funnel options
opts <- list(funnel = list(x = "25%",
                           width = "50%",
                           funnelAlign = "center",
                           max = 500))

pie %>% 
  echart(slices, width = "100%") %>% 
  epie(values, roseType = "radius", radius = list(20, 110)) %>% 
  elegend(orient = "vertical", x = "left", radius = "55%") %>% 
  etoolbox_full() %>% 
  etoolbox_magic(type = list("pie", "funnel"), option = opts) %>% 
  etheme("macarons2")%>% 
  etooltip(trigger = "item") %>% 
  elegend() %>% 
  etitle("Nightingale Rose Chart", "Fake data", x = "center")
```

### Nested 

This is a reproduction of the following [example](http://echarts.baidu.com/echarts2/doc/example/pie3.html#-en) taken from Baidu's EChart official website.

```{r nested}
pie <- data.frame(slice = c("marketing", "IBD", "sales"),
                  values = c(472, 261, 152))

doughnut <- data.frame(slices = c('Direct access', 'mail marketing', 'affiliate ad', 'video ad', 'search engine'),
                  values = c(335, 310, 234, 135, 1548))

pie.lab <- list(normal = list(label = list(position = "inner"),
                              labelLine = list(show = FALSE)))

pie %>% 
  echart(slice, width = "100%") %>% 
  epie(values, radius = list(0, 70), itemStyle = pie.lab) %>% 
  edata(doughnut, slices) %>% 
  epie(values, radius = list(100, 140)) %>% 
  etoolbox_full() %>% 
  elegend(x = "left", orient = "vertical") %>% 
  etheme("macarons")
```

</div>
</main>