---
title: "Toolbox"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(echarts)
```

## What is it?

The toolbox is a set of tools that allows your reader to interact with your chart.

1. Change chart type
2. Switch from stack to tiled charts
3. Save the chart as an image
4. Zoom on an area
5. Mark points on the chart
6. View the data used to plot the chart

## How it works?

Initialise the toolbox with `etoolbox` then add the component(s) you desire.

1. `etoolbox_view`
2. `etoolbox_save`
3. `etoolbox_restore`
4. `etoolbox_mark`
5. `etoolbox_zoom`
6. `etoolbox_magic`

There is also a heper function, `etoolbox_full` that adds a bunch of the above at once.

## Example

```{r}
df <- data.frame(x = 1:20,
                 y = round(runif(20, 5, 10)),
                 z = round(runif(20, 7, 12)),
                 w = round(runif(20, 9, 14)))

df %>% 
  echart(x) %>% 
  ebar(y, stack = "stk") %>% 
  ebar(z, stack = "stk") %>%
  ebar(w) %>%
  etoolbox_full() %>% 
  etoolbox_magic(type = list("line", "bar", "tiled", "stack"))
```